Hadoop Image Processing Framework

### 2015-03-15 Paper.tex
Updated footnotes and references

\begin{document}
\title{Hadoop Image Processing Framework}
\author{\IEEEauthorblockN{Sridhar Vemula}
  \IEEEauthorblockA{Computer Science Department\\
    Oklahoma State University\\
    Stillwater, Oklahoma \\
    Email: sridhar.vemula@okstate.edu}
  \and
  \IEEEauthorblockN{Christopher Crick}
  \IEEEauthorblockA{Computer Science Department\\
    Oklahoma State University\\
    Stillwater, Oklahoma \\
    Email: chriscrick@cs.okstate.edu}
}
\maketitle
\begin{abstract}
With the rapid growth of social media, the number of images being
uploaded to the internet is exploding. Massive quantities of images
are shared through multi-platform services such as Snapchat,
Instagram, Facebook and WhatsApp; recent studies estimate that over
1.8 billion photos are uploaded every day.  However, for the most
part, applications that make use of this vast data have yet to
emerge. Most current image processing applications, designed for
small-scale, local computation, do not scale well to web-sized
problems with their large requirements for computational resources and
storage.  The emergence of processing frameworks such as the Hadoop
MapReduce\cite{Hadoop2009} platform addresses the problem of providing
a system for computationally intensive data processing and distributed
storage. However, to learn the technical complexities of developing
useful applications using Hadoop requires a large investment of time
and experience on the part of the developer.  As such, the pool of
researchers and programmers with the varied skills to develop
applications that can use large sets of images has been limited. To
address this we have developed the Hadoop Image Processing Framework,
which provides a Hadoop-based library to support large-scale image
processing. The main aim of the framework is to allow developers of
image processing applications to leverage the Hadoop MapReduce
framework without having to master its technical details and introduce
an additional source of complexity and error into their programs.
\end{abstract}

@@

\subsection{Downloading and storing image data}
Hadoop uses the Hadoop Distributed File System (HDFS) to store files
in various nodes throughout the cluster.  One of Hadoop's significant
problems is that of small file storage. \cite{White2009} A small file
is one which is significantly smaller than HDFS block size.  Large
image datasets are made up of small image files in great numbers,
which is a situation which HDFS has a great deal of trouble
handling. The problem can be solved by providing a container to group
the files in some way. Hadoop offers a few options:
\begin{itemize}
	\item HAR File
	\item Sequence File
	\item Map File
\end{itemize}

>>>>

\begin{document}
\title{Hadoop Image Processing Framework}
\author{\IEEEauthorblockN{Sridhar Vemula}
  \IEEEauthorblockA{Computer Science Department\\
    Oklahoma State University\\
    Stillwater, Oklahoma \\
    Email: sridhar.vemula@okstate.edu}
  \and
  \IEEEauthorblockN{Christopher Crick}
  \IEEEauthorblockA{Computer Science Department\\
    Oklahoma State University\\
    Stillwater, Oklahoma \\
    Email: chriscrick@cs.okstate.edu}
}
\maketitle
\begin{abstract}
With the rapid growth of social media, the number of images being
uploaded to the internet is exploding. Massive quantities of images
are shared through multi-platform services such as Snapchat,
Instagram, Facebook and WhatsApp; recent studies estimate that over
1.8 billion photos are uploaded every day.  However, for the most
part, applications that make use of this vast data have yet to
emerge. Most current image processing applications, designed for
small-scale, local computation, do not scale well to web-sized
problems with their large requirements for computational resources and
storage.  The emergence of processing frameworks such as the Hadoop
MapReduce\cite{dean2008} platform addresses the problem of providing
a system for computationally intensive data processing and distributed
storage. However, to learn the technical complexities of developing
useful applications using Hadoop requires a large investment of time
and experience on the part of the developer.  As such, the pool of
researchers and programmers with the varied skills to develop
applications that can use large sets of images has been limited. To
address this we have developed the Hadoop Image Processing Framework\footnote[1]{S. Vemula, C. Crick Hadoop Image Processing Framework https://github.com/okstate-robotics/hipl.git},
which provides a Hadoop-based library to support large-scale image
processing. The main aim of the framework is to allow developers of
image processing applications to leverage the Hadoop MapReduce
framework without having to master its technical details and introduce
an additional source of complexity and error into their programs.
\end{abstract}

@@

\subsection{Downloading and storing image data}
Hadoop uses the Hadoop Distributed File System (HDFS)\cite{Shvachko2010} to store files
in various nodes throughout the cluster.  One of Hadoop's significant
problems is that of small file storage. \cite{White2009} A small file
is one which is significantly smaller than HDFS block size.  Large
image datasets are made up of small image files in great numbers,
which is a situation which HDFS has a great deal of trouble
handling. The problem can be solved by providing a container to group
the files in some way. Hadoop offers a few options:
\begin{itemize}
	\item HAR File
	\item Sequence File
	\item Map File
\end{itemize}
